---
title: "Lab 10: Filtering Data"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(fig.height = 5)
knitr::opts_chunk$set(fig.width = 8.5)
knitr::opts_chunk$set(out.width = "100%")
knitr::opts_chunk$set(dpi = 300)

library(readr)
library(ggplot2)
library(dplyr)
library(viridis)
theme_set(theme_minimal())
```

## Pick a dataset

Today you will again have a choice of three datasets to work with. You can
choose either to investigate the daily team ELO ratings in the NBA:

```{r}
nba <- read_csv("https://statsmaths.github.io/stat_data/nba_elo_daily.csv")
```

Metadata from US senator's tweets:

```{r}
tweets <- read_csv("https://statsmaths.github.io/stat_data/senator_tweets_meta.csv")
```

Or swear words given in the movies of Quentin Tarantino:

```{r}
tarantino <- read_csv("https://statsmaths.github.io/stat_data/tarantino.csv")
```

## Analysis
### In this plot the states are on the x axis and the different interactions for tweets are recorded on the y axis. 
```{r}
ggplot(tweets, aes(state, favorites)) +
  geom_point() +
  geom_point(aes(y=retweets)) + 
  geom_point(aes(y=replies)) 

```

### In this plot, all of the states vary in color in order to distinguish them further.
```{r}
ggplot(tweets, aes(state, favorites)) +
  geom_point() +
  geom_point(aes(y=retweets)) + 
  geom_point(aes(y=replies)) +
  geom_point(aes(color=state))
  
```


### This plot highlights interactions in the state of VA, who's representatives are senators Mark Warner and Tim Kaine.

```{r}
virginia <- filter(tweets, state == "VA")
ggplot(virginia, aes(state, favorites)) +
  geom_point() +
  geom_point(aes(y=retweets)) + 
  geom_point(aes(y=replies)) 

```


### In this plot we distinguish between Virginia senators' favorites, retweets, and replies by color.


```{r}
virginia <- filter(tweets, state == "VA")
ggplot(virginia, aes(state, favorites)) +
  geom_point() +
  geom_point(color = "blue", aes(y=retweets)) + 
  geom_point(color = "pink",aes(y=replies)) 
```







