---
title: "Population and Lung Cancer, what's the relationship?"
author: "Lidia Amanuel"
output: html_document
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(out.width = "100%")
knitr::opts_chunk$set(dpi = 300)

library(readr)
library(ggplot2)
library(dplyr)
library(ggmap)
library(forcats)
library(smodels)
library(ggmap)
library(viridis)
```

```{r}
pkgs <- c("viridis")

install.packages(pkgs,
                 repos = "https://cloud.r-project.org",
                 type = "binary",
                 dependencies = TRUE,
                 quiet = TRUE)
```


```{r}
cancer <- read_csv("https://statsmaths.github.io/stat_data/cancer_inc_data.csv")
```

#### Populated areas often have associated characteristics such as air pollution, stress, and environmental detriments carcinogenic exposure. For this reason, I chose to explore whether or not these aspects of urban areas ring true when population isolated from them. Using the CDC's data on lung cancer incidents in adult men per 1000 people, this report will explore this question. Considering localities as being either rural (less than 50,000), suburban (between 50,000 and 200,000), or urban (more than 200,000), population in a locality positively correlates with lung cancer rates in adult men and rural localities. In the following map, we can see the distribution of the rates of lung cancer incidents throughout the US. Due to low rates, and failure to report some localities have been left out from this research analysis. However, we are still able to see that the majority of incidence rates do not exceed 15 percent of the locality. Further, we will look at which of these localities are rural, suburban, or urban and any extremes within those. 


```{r}
qmplot(lon, lat, data = cancer, geom = "blank") +
  geom_point(aes(color = lung), alpha = 1) +
  scale_color_viridis()
```

####  In this regression we see that there isn't a general trend rather there is no correlation between lung cancer incidence rate and population. The r squared value tells us that the regression has no statistical significance. Los Angeles, being the outlier regarding population contributes to the skewing of this regression, however there is little correlation besides that fact. Looking at Los Angeles, it is one of the most urbanized according to population, however there its incidence rate is merely at 5 per cent. Similarly, Union, Florida having the highest incidence rate at 203.7 per 1000 men, falls into the rural categorization. At the extremes, there seems to be a stark negative correlation. 


```{r}
model <- lm_basic(lung ~ 1 + population, data = cancer)
reg_table(model, level = 0.95)
```



```{r}
cancer$pop <- "rural"
cancer$pop[cancer$population < 50000] <- "rural"
cancer$pop[cancer$population > 50000] <- "suburban"
cancer$pop[cancer$population > 200000] <- "urban"
```


```{r}
ggplot(cancer, aes(population, lung)) +
  geom_point(aes(color = factor(pop))) +
  geom_smooth(aes(color = factor(pop)), method = "lm") +
  scale_color_viridis(discrete = TRUE) +
  ylab("Lung Cancer Incidence Rate (per 1000 men)") +
  xlab("Population")

```

#### Because there are more rural areas (by these categorizations), we see a wider range of rural incidence rates, and a more concise view of urban populations. The incomplete gathering of data may have contributed to this as well. In future studies, it would be pertinent to study the different localities with different populations and the living conditions of the locality. 


```{r}
model <- lm_basic(lung ~ 1 + pop, data = cancer)
reg_table(model, level = 0.95)
ggplot(cancer, aes(pop, lung)) +
  geom_violin(color= "pink") +
  ylab("Lung Cancer Incidence Rate (per 1000 men)") +
  xlab("Population")
```



```{r}
ggplot(cancer, aes(pop)) +
  geom_bar()+
  ylab("Count") +
  xlab("Type of Locality")
```

